Makefile, compiliation notes

### 2018-05-16 Paper.Rmd
some changes and asym sens description completed

csl: ecology-letters.csl
bibliography: REF_ALL.bib
---
updated on `r Sys.Date()`
```{r setup_Paper, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
seed<-101
# families<-c(1,3:10,13,14,16:20)
source("mtime.R") #A function needed for caching
```
# Front matter

@@

```{r fig_stat_testing_save_and_plot_result, message=F, results="hide", echo=F, cache=T, cache.extra=list(seed,mtime("TestStats_multivar_dataset.R"),mtime("CopulaFunctions.R"),mtime("CopulaFunctions_flexible.R"),mtime("StatTestNumericResults.RData"))}
set.seed(seed) 
source("fig_Paper_stat_testing.R")
load("./Results/stat_results/stat_testing/StatTestNumericResults.RData")
resultsloc<-"./Results/stat_results/stat_testing/"

copname<-"C"
reslist<-res_pt35_rankT

statname<-"CorlmCoru"
call_fig_Paper_stat_testing(resultsloc=resultsloc,statname=statname,copname=copname,reslist=reslist, numsims=100)
statname<-"PlmPu"
call_fig_Paper_stat_testing(resultsloc=resultsloc,statname=statname,copname=copname,reslist=reslist, numsims=100)
statname<-"D2umD2l"
call_fig_Paper_stat_testing(resultsloc=resultsloc,statname=statname,copname=copname,reslist=reslist, numsims=100)
```

@@

We simulated our model (\ref{eq.AS}) for different values of $b$ with $a=0.2$, $r=0.8$. $N=10000$ points were generated from each local and global fluctuations to apply on the initial populations and then after simulation we kept only last $1000$ populations to plot the copula for a specific $b$ and a specific functional form of $g$. Fig. \ref{SM-fig_ms_asym_b_0.1} and Fig. \ref{SM-fig_ms_asym_b_0.9} show these results. We also carried out model selection and non-parametric statistical analysis with each copula of those figures and summarized our results in Tables \ref{SM-tab_summary_stat_asym_sens} - \ref{SM-tab_stat_npa_asym_8}. Table \ref{SM-tab_summary_stat_asym_sens} shows that according to our model selection approach for $b=\pm0.1$, non-normal copula (with higher AIC weights) were always best-fit with some asymetric tail dependence.

>>>>

csl: ecology-letters.csl
bibliography: REF_ALL.bib
---
updated on `r Sys.Date()`
```{r setup_Paper, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
#seed<-101
#source("mtime.R") #A function needed for caching
```
# Front matter

@@

@@

We simulated our model (\ref{eq.AS}) for different values of $b$ with $a=0.2$, $r=0.8$. $10000$ points were generated from each local and global fluctuations to apply on the initial populations and then after simulation we kept only last $1000$ time step of simulation to plot the population-copula for a specific $b$ and a specific functional form of $g$  (For code see [`Simulator_asym_sens`](https://github.com/sghosh89/BIVAN/blob/master/asym_sensitivity.R) function). Fig. \ref{SM-fig_ms_asym_b_0.1} and Fig. \ref{SM-fig_ms_asym_b_0.9} show these results for $b=\pm0.1$ and $b=\pm0.9$, respectively. We also carried out model selection and non-parametric statistical analysis with each copula of those figures and summarized our results in Tables \ref{SM-tab_summary_stat_asym_sens} - \ref{SM-tab_stat_npa_asym_8}. Table \ref{SM-tab_summary_stat_asym_sens} represent the model selection results with AIC weights for best fitted copula and normal copula, model averaged lower and upper tail dependence, p-values (both Cramer-von Mises statistic and Kolmogorov-Smirnov statistic) for goodness of fit test. In each case, successful bootstrap was $100\%$. According to our model selection approach, for $b=\pm0.1$, non-normal copula (with higher AIC weights) were always best-fit with some asymetric tail dependence whereas for $b\pm0.9$, most of the time normal was best. It is probably because the populations get long-time exposure to environmental changes for slower growth(or decay) rate and so global fluctuation can affect them more efficiently. Our non-parametric analysis results (Tables \ref{SM-tab_stat_npa_asym_1} -\ref{SM-tab_stat_npa_asym_8}) are consistent with this model selection approach.

### 2018-05-16 SupportingInformation.Rmd
some changes and asym sens description completed

<!--checkpoint package-->
```{r checkpoint_chunk, echo=F, warning=F, message=F, results="hide"}
library(checkpoint)
library(captioner)
if (!dir.exists("./.checkpoint/")){
  dir.create("./.checkpoint/")
}
checkpoint("2018-03-29",checkpointLocation = "./")
```

@@

>>>>

<!--checkpoint chunk is moved to makefile.Rmd-->

@@

<!--This r-chunk generates figure necessary for maintext Paper-->
```{r fig_stat_testing_for_maintext, message=F, results="hide", echo=F, cache=T, cache.extra=list(seed,mtime("TestStats_multivar_dataset.R"),mtime("CopulaFunctions.R"),mtime("CopulaFunctions_flexible.R"),mtime("StatTestNumericResults.RData"))}
set.seed(seed) 
source("fig_Paper_stat_testing.R")
#load("./Results/stat_results/stat_testing/StatTestNumericResults.RData")
resultsloc<-"./Results/stat_results/stat_testing/"

copname<-"C"
reslist<-res_pt35_rankT

statname<-"CorlmCoru"
call_fig_Paper_stat_testing(resultsloc=resultsloc,statname=statname,copname=copname,reslist=reslist, numsims=100)
statname<-"PlmPu"
call_fig_Paper_stat_testing(resultsloc=resultsloc,statname=statname,copname=copname,reslist=reslist, numsims=100)
statname<-"D2umD2l"
call_fig_Paper_stat_testing(resultsloc=resultsloc,statname=statname,copname=copname,reslist=reslist, numsims=100)
```

### 2018-05-16 makefile.Rmd
some changes and asym sens description completed

---
title: "Makefile_linux, compiliation notes"
author: "Daniel Reuman"
date: ""
output: pdf_document
---

>>>>

---
title: "Makefile, compiliation notes"
author: "Daniel Reuman"
date: ""
output: pdf_document
---
<!--checkpoint package-->
```{r checkpoint_chunk, echo=F, warning=F, message=F, results="hide"}
library(checkpoint)
library(captioner)
library(rmarkdown)
if (!dir.exists("./.checkpoint/")){
  dir.create("./.checkpoint/")
}
checkpoint("2018-03-29",checkpointLocation = "./")
```
